---
title: "ESM228_Practicum3"
author: "Bridget Gibbons"
date: "5/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo = TRUE, message = FALSE}

library(DeclareDesign)
library(truncnorm)
library(knitr)
library(ggplot2)
library(dplyr)

```

##declare_population()

```{r declare population, echo = TRUE}

set.seed(101)
population <- declare_population(
  sb_hotels = add_level(N=150, 
    baseline_water = runif(n=N, min=80, max=500), #min and max values measured
    annual_change_rate = rnorm(n=N, mean=1.02, sd=0.05)) #annual rate of change is 1.1 with sd of 0.2
)
pop <- population()

```

##declare_potential_outcomes()

```{r declare potential outcomes, echo=TRUE}

potential_outcomes <- 
  declare_potential_outcomes(
    Y_Z_0 = baseline_water * annual_change_rate, 
    Y_Z_1 = baseline_water * annual_change_rate * 0.97) 
po <- potential_outcomes(pop)
```

##Checking to see the population created:

```{r po-see, echo=FALSE}
kable(po[1:5,], digits=2) #this is what the table will look like with this population
```

```{r po-check, echo=TRUE}

mean(po$baseline_water)

sd(po$baseline_water)

```


## declare_sampling()

Next, we want to select the sample size:

```{r sample, echo=TRUE}
sampling <- declare_sampling(n=150) #start with randomly sampling 150 hotels (all in SB)
sam <- sampling(po)
```


## declare_assignment()

We now want to assign one third of the units to treatment.

```{r assign, echo=TRUE}
assigning <- declare_assignment(m=50)
assigned <- assigning(sam)
kable(assigned[1:5,c(1:2,4:5,7)], 
      digits = 1) #look at the object after sampling
```


## declare_reveal()

This step declares how the potential outcomes are revealed by the random assignment

```{r reveal, echo=TRUE}
revealing <- declare_reveal() #reveals which of the two potential outcomes you see
```


## declare_estimand()

Recall that we set the treatment effect as a 10% reduction in water use (gallons per day per room) relative to the control group.

```{r estimand, echo=TRUE}
estimand <- declare_estimand(
  prop.change = mean((Y_Z_1-Y_Z_0)/baseline_water)) #estimand is overall change between treated and untreated outcome with respect to the baseline
estimand(po)
```


## declare_estimator()

Here we are going to take as our outcome the ratio of endline:baseline WQI

```{r estimator, echo=TRUE}
dip <- declare_estimator(Y*(1/baseline_water) ~ Z, 
                         estimand = estimand,  
          model =  lm_robust, label = "DIP") # (difference in proportions)
```


## declare_design()

This function brings all of the parts of the process together in a single design and allows for each part of the design to be simulated repeatedly.

```{r design, echo=TRUE}
design <- population + potential_outcomes + sampling +
          assigning + revealing + estimand + dip


```


## diagnose_design()

At this stage, we can calculate various features of the design that we have specified:

```{r diagnosis, cache=TRUE}
diagnosis <- diagnose_design(design)
diagnosis$diagnosands_df[,c(1,3,5,9,11)] %>%
  kable()
```


